---
title: "Figures - Estimating SATE with Regression Estimator"
author: "Charlotte Mann"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(dplyr)
library(kableExtra)
library(ggplot2)
library(latex2exp)
library(RColorBrewer)
library(xtable)
library(stringr)
```

Order the estimators for tables and plots.

```{r}
mod.order <- c("dif.mean", "reg.est",
               "re.g", 
               "re.gtilde",  
               "re.gdp1", "re.gdp3", "re.gdp6",
               "re.gdp10","re.gdp15",
               "re.syn",
               "re.syn.dp")

mod.names <- c("Difference in Means", "RCT Covs", 
               "G",
               "G-tilde",
               "G*, e=1", "G*, e=3", "G*, e=6",
               "G*, e=10", "G*, e=15",
               "Synthetic",
               "DP synthetic")
```

Load datasets from GreatLakes.

```{r}
load("sim-out/sim-result-10.Rdata")
load("sim-out/sim-result-20.Rdata")
load("sim-out/sim-result-50.Rdata")
```

## P = 10

MSE of gram matrix for different noise additions:
```{r, echo=F}
apply(gmse.p10,2,mean)
```
Table of estimated variances:
```{r p10, echo = F}
plot.dat <- out.p10 %>%
  mutate(RE_sd = 1/RE_sd, RE_reg = 1/RE_reg) %>%
  group_by(mod) %>%
  summarize(across(everything(), list(mean = mean, se = ~sd(.x)/sqrt(100))))

table_1 <- plot.dat %>%
  select(mod, est_mean = est_mean_mean, est_var = est_var_mean, RE_sd = RE_sd_mean, RE_reg = RE_reg_mean, RE_sd_se, RE_reg_se) %>%
  mutate(sd_var = case_when(mod == "dif.mean" ~ est_var,
                                TRUE ~ NA_real_),
         reg_var = case_when(mod == "reg.est" ~ est_var,
                                TRUE ~ NA_real_)) %>%
  ungroup() %>%
  mutate(sd_var = mean(sd_var, na.rm = T),
         reg_var = mean(reg_var, na.rm = T)) %>%
  mutate(RE_sd2 = est_var/sd_var, RE_reg2 = est_var/reg_var) %>%
  mutate(RE_sd = case_when(RE_sd_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_sd, RE_sd_se),
                           TRUE ~ sprintf("%1.2f", RE_sd)),
         RE_reg = case_when(RE_reg_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_reg, RE_reg_se),
                           TRUE ~ sprintf("%1.2f", RE_reg)))

table_1$mod <- factor(table_1$mod, levels = mod.order)
table_1 <- table_1[order(table_1$mod),]

table_1 %>% 
  select(mod, est_var, RE_sd, RE_reg) %>%
  knitr::kable(format = "markdown", digits =3,
               col.names = c("Estimator", "Var","RE v SD", "RE v Reg"))
```

```{r}
xtab <- table_1 %>%
  select(est_var, RE_sd, RE_reg) %>%
  xtable(caption = "", table.placement = "ht",
               digits = c(0,3,0,0))
print(xtab, comment = F, size="footnotesize",
      file='../figures/var-sim-reg-p10.tex', include.rownames = F)
```

## P = 20

MSE of gram matrix for different noise additions:
```{r, echo=F}
apply(gmse.p20,2,mean)
```
Table of estimated variances:
```{r p20,echo=F}
plot.dat <- out.p20 %>%
  mutate(RE_sd = 1/RE_sd, RE_reg = 1/RE_reg) %>%
  group_by(mod) %>%
  summarize(across(everything(), list(mean = mean, se = ~sd(.x)/sqrt(100))))

table_1 <- plot.dat %>%
  select(mod, est_mean = est_mean_mean, est_var = est_var_mean, RE_sd = RE_sd_mean, RE_reg = RE_reg_mean, RE_sd_se, RE_reg_se) %>%
  mutate(sd_var = case_when(mod == "dif.mean" ~ est_var,
                                TRUE ~ NA_real_),
         reg_var = case_when(mod == "reg.est" ~ est_var,
                                TRUE ~ NA_real_)) %>%
  ungroup() %>%
  mutate(sd_var = mean(sd_var, na.rm = T),
         reg_var = mean(reg_var, na.rm = T)) %>%
  mutate(RE_sd2 = est_var/sd_var, RE_reg2 = est_var/reg_var) %>%
  mutate(RE_sd = case_when(RE_sd_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_sd, RE_sd_se),
                           TRUE ~ sprintf("%1.2f", RE_sd)),
         RE_reg = case_when(RE_reg_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_reg, RE_reg_se),
                           TRUE ~ sprintf("%1.2f", RE_reg)))

table_1$mod <- factor(table_1$mod, levels = mod.order)
table_1 <- table_1[order(table_1$mod),]

table_1 %>% 
  select(mod, est_var, RE_sd, RE_reg) %>%
  knitr::kable(format = "markdown", digits =3,
               col.names = c("Estimator", "Var","RE v SD", "RE v Reg"))
```

```{r}
xtab <- table_1 %>%
  select(est_var, RE_sd, RE_reg) %>%
  xtable(caption = "", table.placement = "ht",
               digits = c(0,3,0,0))
print(xtab, comment = F, size="footnotesize",
      file='../figures/var-sim-reg-p20.tex', include.rownames = F)
```


## P = 50

MSE of gram matrix for different noise additions:
```{r, echo=F}
apply(gmse.p50,2,mean)
```
Table of estimated variances:
```{r p50,echo=F}
plot.dat <- out.p50 %>%
  mutate(RE_sd = 1/RE_sd, RE_reg = 1/RE_reg) %>%
  group_by(mod) %>%
  summarize(across(everything(), list(mean = mean, se = ~sd(.x)/sqrt(100))))

table_1 <- plot.dat %>%
  select(mod, est_mean = est_mean_mean, est_var = est_var_mean, RE_sd = RE_sd_mean, RE_reg = RE_reg_mean, RE_sd_se, RE_reg_se) %>%
  mutate(sd_var = case_when(mod == "dif.mean" ~ est_var,
                                TRUE ~ NA_real_),
         reg_var = case_when(mod == "reg.est" ~ est_var,
                                TRUE ~ NA_real_)) %>%
  ungroup() %>%
  mutate(sd_var = mean(sd_var, na.rm = T),
         reg_var = mean(reg_var, na.rm = T)) %>%
  mutate(RE_sd2 = est_var/sd_var, RE_reg2 = est_var/reg_var) %>%
  mutate(RE_sd = case_when(RE_sd_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_sd, RE_sd_se),
                           TRUE ~ sprintf("%1.2f", RE_sd)),
         RE_reg = case_when(RE_reg_se > .015 ~ sprintf("%1.2f (%1.2f)", RE_reg, RE_reg_se),
                           TRUE ~ sprintf("%1.2f", RE_reg)))

table_1$mod <- factor(table_1$mod, levels = mod.order)
table_1 <- table_1[order(table_1$mod),]

table_1 %>% 
  select(mod, est_var, RE_sd, RE_reg) %>%
  knitr::kable(format = "markdown", digits =3,
               col.names = c("Estimator", "Var","RE v SD", "RE v Reg"))
```

```{r}
xtab <- table_1 %>%
  select(est_var, RE_sd, RE_reg) %>%
  xtable(caption = "", table.placement = "ht",
               digits = c(0,3,0,0))
print(xtab, comment = F, size="footnotesize",
      file='../figures/var-sim-reg-p50.tex', include.rownames = F)
```

### Plot format for presentations

```{R}
all.out <- out.p10 %>%
  mutate(p = "P = 10") %>%
  bind_rows(out.p20) %>%
  mutate(p = case_when(is.na(p) ~ "P = 20",
                       TRUE ~ p)) %>%
  bind_rows(out.p50) %>%
  mutate(p = case_when(is.na(p) ~ "P = 50",
                        TRUE ~ p)) %>%
  select(mod, p, est_mean, est_var, RE_sd, RE_reg) %>%
  group_by(mod, p) %>%
  summarize(across(everything(), list(mean = mean, se = ~sd(.x)/sqrt(100))))

plot.dat <- all.out %>%
  select(mod,p, est_mean = est_mean_mean, est_var = est_var_mean, RE_sd = RE_sd_mean, RE_reg = RE_reg_mean, RE_sd_se, RE_reg_se) %>%
  ungroup() %>%
  mutate(sd_var = case_when(mod == "dif.mean" ~ est_var,
                                TRUE ~ NA_real_),
         reg_var = case_when(mod == "reg.est" ~ est_var,
                                TRUE ~ NA_real_)) %>%
  group_by(p) %>%
  mutate(sd_var = mean(sd_var, na.rm = T),
         reg_var = mean(reg_var, na.rm = T)) %>%
  mutate(RE_sd2 = sd_var/est_var, RE_reg2 = reg_var/est_var) %>%
  mutate(ub = RE_reg + 2*RE_reg_se, lb = RE_reg - 2*RE_reg_se) %>%
  mutate(type = case_when(str_detect(mod,"gdp") ~ "GDP",
                          mod %in% c("dif.mean","reg.est") ~ "RCT",
                          str_detect(mod,"syn") ~ "synth",
                          mod == "re.gtilde" ~ "gtilde",
                          TRUE ~ "g"
                          )) %>%
  arrange(p, RE_reg) %>%
  group_by(p) %>%
  mutate(id = row_number())


```


```{r}
mod.names.tikz <- c("Dif in Means", "RCT Covs", 
               "$\\bm G$",
               "$\\tilde{\\bm G}$",
               "$\\bm G^{*}, \\epsilon=1$", "$\\bm G^{*}, \\epsilon=3$", "$\\bm G^{*}, \\epsilon=6$",
               "$\\bm G^{*}, \\epsilon=10$", "$\\bm G^{*}, \\epsilon=15$",
               "Synthetic ($\\tilde{\\bm D}$)",
               "DP Synthetic ($\\bm D^{*}$)")

plot.dat$mod <- factor(plot.dat$mod, levels = mod.order)
```

```{r}
cols <- c("#fd8d3c","#f768a1",
          "#8c6bb1",
          "#6e016b",
          "#a1d99b","#74c476","#41ab5d","#238b45","#005a32",
          "#4292c6","#08306b")
 
shapes <- c(19, 19,
            18,
            17,
            17,17,17,17,17,
            15,15)
```


```{r}
g <- ggplot(data = plot.dat, 
            aes(x = id, y = RE_reg, color = mod, shape = mod)) +
  geom_hline(yintercept = 1)+
  geom_point(size =3)+ facet_wrap(~p)+
  xlab("") + 
  scale_color_manual(name="", values = cols, labels = mod.names)+
  scale_shape_manual(name="", values = shapes, labels = mod.names) +
  #ggtitle("P = 20")+
  scale_y_continuous(name="Relative Efficiency", breaks =c(.5,.75,1,1.25, 1.5, 1.75, 2), limits=c(.3,2.11))+
  theme(text = element_text(family = "sans",
                            size = 10),
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        strip.text = element_text(size = 10),
        legend.position = "right",
        axis.ticks.x = element_blank(),
        legend.text = element_text(size = 10))
  
g
```


```{r}
png("../figures/re-regression.png", width = 10, height = 4, units = 'in', res = 300)
g
dev.off()
```

### defense slides

```{r}
g <- ggplot(data = plot.dat) +
  geom_hline(yintercept = 1) +
  #geom_errorbar(aes(x = id, ymin = lb, ymax = ub), width = .5, linewidth = .2)+
  geom_point(aes(x = id, y = RE_reg, color = mod, shape = mod), size =2)+ 
  facet_wrap(~p)+
  xlab("") + 
  scale_color_manual(name="", values = cols, labels = mod.names)+
  scale_shape_manual(name="", values = shapes, labels = mod.names) +
  #ggtitle("P = 20")+
  scale_y_continuous(name="Relative Efficiency", breaks =c(.5,.75,1,1.25, 1.5, 1.75, 2), limits=c(.3,2.2))+
  theme(text = element_text(family = "sans",
                            size = 10),
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 6),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        strip.text = element_text(size = 8),
        legend.position = "right",
        legend.justification="top",
        axis.ticks.x = element_blank(),
        legend.box.spacing = unit(0, 'cm'),
        legend.text = element_text(size = 8),
        legend.margin=ggplot2::margin(-10,0,0,7),
        plot.margin = unit(c(0, 0, 0, 0),"inches"))

g
```


```{r}
tikz(file = "../figures/re-regression-pres-all.tex", width = 5.7, height = 2.7, bg = "transparent")
g
dev.off()
```

```{r}
g <- ggplot(data = plot.dat) +
  geom_hline(yintercept = 1) +
  geom_errorbar(aes(x = id, ymin = lb, ymax = ub), width = .5, linewidth = .2)+
  geom_point(aes(x = id, y = RE_reg, color = mod, shape = mod), size =2)+ 
  facet_wrap(~p)+
  xlab("") + 
  scale_color_manual(name="", values = cols, labels = mod.names)+
  scale_shape_manual(name="", values = shapes, labels = mod.names) +
  #ggtitle("P = 20")+
  scale_y_continuous(name="Relative Efficiency", breaks =c(.5,.75,1,1.25, 1.5, 1.75, 2), limits=c(.3,2.2))+
  theme(text = element_text(family = "sans",
                            size = 10),
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 6),
        axis.title.y = element_text(size = 8),
        axis.title.x = element_text(size = 8),
        strip.text = element_text(size = 8),
        legend.position = "right",
        legend.justification="top",
        axis.ticks.x = element_blank(),
        legend.box.spacing = unit(0, 'cm'),
        legend.text = element_text(size = 8),
        legend.margin=ggplot2::margin(-10,0,0,7),
        plot.margin = unit(c(0, 0, 0, 0),"inches"))

g
```

```{r}
tikz(file = "../figures/re-regression-pres-all-werrrors.tex", width = 5.7, height = 2.7, bg = "transparent")
g
dev.off()
```

## simplified

```{r}
simp <- list()
simp[["1"]] <- c("reg.est", "dif.mean")
simp[["2"]] <- c("reg.est", "dif.mean", "re.g")
simp[["3"]] <- c("reg.est", "dif.mean", "re.g","re.syn.dp","re.syn")
simp[["4"]] <- c("reg.est", "dif.mean", "re.g","re.syn.dp","re.syn","re.gtilde")


mod.order <- c("dif.mean", "reg.est",
               "re.g", 
               "re.gtilde",  
               "re.gdp1", "re.gdp3", "re.gdp6",
               "re.gdp10","re.gdp15",
               "re.syn",
               "re.syn.dp")

mod.names <- c("Difference in Means", "RCT Covs", 
               "G",
               "G-tilde",
               "G*, e=1", "G*, e=3", "G*, e=6",
               "G*, e=10", "G*, e=15",
               "Synthetic",
               "DP synthetic")
```

```{r}

for(x in 1:4){
  
  idx <- which(mod.order %in% simp[[x]])
  
  g <- ggplot(data = plot.dat %>% filter(comparison == "Regression" & (mod 
                                       %in% simp[[as.character(x)]])), 
            aes(x = id, y = val, color = mod, shape = mod)) +
  geom_hline(yintercept = 1)+
  geom_point(size =3)+ facet_wrap(~p)+
  xlab("") + 
  #ylab("Relative Efficiency") +
  scale_color_manual(name="", values = cols[idx], labels = mod.names[idx])+
  scale_shape_manual(name="", values = shapes[idx], labels = mod.names[idx]) +
  scale_y_continuous(name="Relative Efficiency", breaks =c(.5,.75,1,1.5,2,2.5,3), limits=c(.4,3.1))+
  #ggtitle("P = 20")+
  #ylim(.32,2.12)+
  theme(text = element_text(family = "sans",
                            size = 10),
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        strip.text = element_text(size = 10),
        legend.position = "right",
        axis.ticks.x = element_blank(),
        legend.text = element_text(size = 10))
  

  
  png(paste0("../figures/re-regression-simp-",x,".png"), width = 10, height = 4, units = 'in', res = 300)
  print(g)
  dev.off()
}

```